### 2014-08-30 fundamentals/qa.tex
added testing section

% Unfortunately, we can't wind forward the clock to compare our simulations to 
% the futures that we are attempting to model.

% However, Cyclus does implement a number of strategies for verification and 
% validation of code.

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs

Some routines are implemented specifically to ensure robustness.

\subsection{Testing}
% Peer-review system (secretly a note on open source?)

We have reasonable test coverage and a code review system.

@@

Testing individual units of 'work'.

@@

Testing identical output for each pull request.

Testing aggregate answers for each pull request. Specifically, previous
simulations used in publications are integration tested to confirm their output
is maintained.

>>>>

\subsection{Testing}

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign that the
simulator does or does not work as intended on a new system.
Testing serves a critical role in QA because it directly compares the 
results of running software versus the expected behavior of the software.
In cyclus, three categories of tests are defined: unit tests, integration 
tests, and regression tests.

It is important to note that before a proposed
code changes is allowed into main stream cyclus, all of the tests must pass
and the change must be covered by a test, either new or existing. This is 
matter of policy for the developers. Additionally, test code is equally likely 
as the code it is testing to contain errors. To prevent an infinite recurrsion 
of testing-the-tests, it is assumed that dilligence and one level of testing 
is sufficient to meet the aims of the quality assurance.

@@

Unit tests are those which compare the results of the smallest code \emph{unit}, 
typically a single function or a class. What constitutes a the smallest code
unit depends on the context of the specific unit in question. While this is 
an ambiquous defintiion, combined with a philosophy of keeping units as small
as possible it is often clear in practice what needs to be tested.

Cyclus uses the Google Test framework \cite{gtest} as a harness for running unit 
tests. Sufficient unit tests are required for any proposed change to the cyclus
code base. Currently cyclus implements over 450 unit tests and cycamore has 
85.  These cover approximately 65\% of their respective code bases. This number 
is expected to grow over time.

Intergration tests are any tests that combine multiple elemnents of the 
cyclus interface and test that they work correctly with each other.  By analogy, 
simply because the gears (units) are made correctly does not imply that the 
clock (integration) will run smoothly, run at all, or give the correct time.
In cyclus and cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of 
time. Precanned input files have thus been contsructed. Their results 
are inspected and compared via nose \cite{nosetests}, a Python test framework.
Python will run cyclus as a subprocess for each integration test. In this
way cyclus code units are tested in the full context that they will
executed. This category of testing is especially useful for ensuring that 
major cyclus components are functioning as expected.

@@

Regression tests are tests which ensure that significant changes do not 
occur over the course of cyclus development. Such a change is called a 
\emph{regression} because the new version is almost always wrong.
Regression tests are implemeneted similarly to integration tests.
Nose is used to execute fully fledged cyclus simulations whose results
are then compared. In this category however the comparison is done against 
the output of the same input file when run with a previous version of cyclus, 
typically the last released version.
In some sense, regression tests are `dumb' in that they do 
not care about the contents of a simulation being correct, only whether or not 
it changed. They thus pick up glaring time-sensitive mistakes that may 
not appear elsewhere though they do not purport to make claims about the
quality of the physics modeled. The cycamore project is the primary location of
regression tests. This is because the archetypes here are sophisticated enough
to make interesting input files. Only a handful ($<10$) time steps are needed 
for regression testing.
